Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs

### 2022-02-24 paper/appendix.Rmd
minor updates to manuscript

```{r, echo=FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```

@@

```{r range, fig.cap=range_cap, fig.height=10}
loadd(p_range)

plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
```

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```

@@

```{r range, fig.cap=range_cap, fig.height=10}
loadd(p_range)
plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
```

### 2022-02-24 paper/manuscript.Rmd
minor updates to manuscript

```{r}
loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
```
```{r}
nb_st <- unique(slope_com_var_no_covar$station) %>% length
rm(slope_com_var_no_covar)
nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
```

>>>>

```{r}
loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
loadd(range_data)
```
```{r}
nb_st <- unique(slope_com_var_no_covar$station) %>% length
rm(slope_com_var_no_covar)
nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
```
